Continuous Generalization of Buildings

### 2017-01-12 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
added the text about "An idea of continuously generalising buildings"

\section{Introduction}
\label{sec:Introduction}

@@

Text.

>>>>

\section{An idea of continuously generalising buildings}
We have an input map at scale $1:15 \mathrm{k}$.
We want to generate, by generalisation, $10$ maps which are at 
scale $1:20\mathrm{k}$, $1:25\mathrm{k}$, 
$1:30\mathrm{k}$, $\dots$, $1:65\mathrm{k}$.
We always produce a map by generalising the 
immediate-larger-scale map. For example, we produce the map at 
scale $1:25\mathrm{k}$ by generalising, instead of the input 
map, the map at scale $1:20\mathrm{k}$.
This production 
guarantees consistency. Namely, if a building does not exist on 
a map at a certain scale, then the building will never exist on 
a map at a smaller scale.

We have two requirements for an output map.
The first one is that the distance between two 
buildings should be at least $d$.
The second requirement is that a building with area less than 
$d^2$ should be eliminated.
In order to make sure that some small buildings will be 
eliminated, the radius $r$ that we use to buffer buildings 
should be smaller than $d$. We simply use $r=\frac{1}{2}d$.
Our buildings may have been buffered with radius, in total, $r_0 
(r_0 < r)$ from previous steps.
Therefore, we only need to buffer with radius $r-r_0$ at the new 
step.

Our generalisation is as follows. We buffer buildings with 
radius $d+r-r_0$, then we buffer the results with $-d$. In order 
to 
remove some spikes from the buffering, we buffer the results 
with $-\epsilon$, and then again with $\epsilon$. We simply set 
$\epsilon=\frac{1}{10}d$. After these buffering operations, we 
eliminate the buildings with area less than $d^2$.

@@
